Manuscript title here

### 2021-06-01 doc/ms/ms.Rmd
update manuscript. Almost finalized figures and results. Moving on to discussion.

source("./packages.R")
drake::loadd(temperature_stats)

@@

pb_skew_summ = skew_analysis[["PB_skew_summ"]]

@@

The fluxes of OM were distributed differently across body sizes and turnover rates (*P:B*) among and within streams. Across streams, mean body size of taxa ranged from `r m_summ %>% slice_min(M_mg_ind_mean) %>% select(M_mg_ind_mean)%>% round(2)` to `r m_summ %>% slice_max(M_mg_ind_mean) %>% select(M_mg_ind_mean)%>% round(2)` and mean annual P:B ranged from `r pb_summ %>% slice_min(pb_y_mean) %>% select(pb_y_mean)%>% round(2)` to `r pb_summ %>% slice_max(pb_y_mean) %>% select(pb_y_mean)%>% round(2)` (Figure 2). Both, *M* and *P:B* showed associations with mean annual stream temperature that were negative and positive, respectively. Generally, mean *M* of the community decreased `r M_temp_coef_mean`% (95% PI, `r M_temp_coef_quant2.5`% -- `r M_temp_coef_quant97.5`%) for each increase in 1$^\circ$C. In contrast, mean population *P:B* of the community increased `r pb_temp_coef_mean`% (95% IP, `r pb_temp_coef_quant2.5`% -- `r pb_temp_coef_quant97.5`%) for each 1$^\circ$C in mean annual stream temperature. Fluxes were skewed differentially towards larger body sizes (positive skew) or towards smaller body sizes (negative skew) among streams, with skew estimates with body size (*M*) ranging from `r m_skew_summ %>% slice_min(abs(M_mg_ind_skew_mean)) %>% select(M_mg_ind_skew_mean)%>% round(2)` to `r m_skew_summ %>% slice_max(abs(M_mg_ind_skew_mean)) %>% select(M_mg_ind_skew_mean)%>% round(2)` (Figure 3). Similarly, skew in fluxes towards high turnover taxa varied among streams ranging from `r pb_skew_summ %>% slice_min(abs(pb_y_skew_mean)) %>% select(pb_y_skew_mean)%>% round(2)` to `r pb_skew_summ %>% slice_max(abs(pb_y_skew_mean)) %>% select(pb_y_skew_mean) %>% round(2)` (Figure 3).

We compared the empirical $Sk_{flux}$ measurement within streams to a random ordering to detect random vs. non-random structure in the community energy fluxes. the probability of observing a similar or more extreme skew of within stream OM fluxes in relation to species body size ranged from `r m_skew_summ %>% select(matches("M.*prob_mean")) %>% min%>% round(2)` to `r m_skew_summ %>% select(matches("M.*prob_mean")) %>% max%>% round(2)`. Similarly, the probability of a more extremely skewed distribution in relation to population biomass turnover ranged from `r pb_skew_summ %>% select(matches("pb.*prob_mean")) %>% min%>% round(2)` to `r pb_skew_summ %>% select(matches("pb.*prob_mean")) %>% max%>% round(2)`. The probability that

The skew of energy fluxes towards populations with smaller/larger body sizes or higher/lower turnover showed weak, yet systematic variation with stream temperature (Figure XX). Skew towards larger body sizes was negatively association with stream temperature. The mean effect size of increasing temperature was to shift the skewness coefficient, $Sk_{flux}$, `r M_skew_temp_coef_mean` units (`r M_skew_temp_coef_quant2.5` to `r M_skew_temp_coef_quant97.5` 95% PI) for every 1 $^\circ$C . The estimated effect of temperature on $Sk_{flux}$ towards higher body size populations exhibited a bimodal distribution around zero, but `r ((sum(M_skew_temp_coefs < 0)/n_boot)*100)`% of values fell below zero. Similarly, energy fluxes through the community skewed increasingly toward higher turnover (*P:B*)organisms with increasing temperature. The increase in $Sk_{flux}$ towards higher *P:B* populations was `r pb_skew_temp_coef_mean` (`r pb_skew_temp_coef_quant2.5` to `r pb_skew_temp_coef_quant97.5` 95% PI).

@@

>>>>

source("./packages.R")
drake::loadd(temperature_stats)
n_boot = temperature_stats[['n_boot']]

@@

pb_skew_summ = skew_analysis[["pb_skew_summ"]]

@@

The fluxes of OM were distributed differently across body sizes and turnover rates (*P:B*) among and within streams. Across streams, mean body size of taxa ranged from `r m_summ %>% slice_min(M_mg_ind_mean) %>% select(M_mg_ind_mean)%>% round(2)` to `r m_summ %>% slice_max(M_mg_ind_mean) %>% select(M_mg_ind_mean)%>% round(2)` and mean annual P:B ranged from `r pb_summ %>% slice_min(pb_y_mean) %>% select(pb_y_mean)%>% round(2)` to `r pb_summ %>% slice_max(pb_y_mean) %>% select(pb_y_mean)%>% round(2)` (Figure 2). Both, *M* and *P:B* showed associations with mean annual stream temperature that were negative and positive, respectively. Generally, mean *M* of the community decreased `r M_temp_coef_mean`% (95% PI, `r M_temp_coef_quant2.5`% -- `r M_temp_coef_quant97.5`%) for each increase in 1$^\circ$C. In contrast, mean population *P:B* of the community increased `r pb_temp_coef_mean`% (95% IP, `r pb_temp_coef_quant2.5`% -- `r pb_temp_coef_quant97.5`%) for each 1$^\circ$C in mean annual stream temperature. Energy fluxes within consumer communities were skewed towards larger body sizes (positive skew), towards smaller body sizes (negative skew), or neutrally in regards to body size  among streams, with skew estimates with body size (*M*) ranging from `r m_skew_summ %>% slice_min(abs(M_mg_ind_skew_mean)) %>% select(M_mg_ind_skew_mean)%>% round(2)` to `r m_skew_summ %>% slice_max(abs(M_mg_ind_skew_mean)) %>% select(M_mg_ind_skew_mean)%>% round(2)` (Figure 3). Similarly, skew in fluxes towards high turnover taxa varied among streams ranging from `r pb_skew_summ %>% slice_min(abs(pb_y_skew_mean)) %>% select(pb_y_skew_mean)%>% round(2)` to `r pb_skew_summ %>% slice_max(abs(pb_y_skew_mean)) %>% select(pb_y_skew_mean) %>% round(2)` (Figure 3).

We compared the empirical $Sk_{flux}$ measurement within streams to a random ordering to detect random vs. non-random structure in community energy fluxes. The probability of observing a similar or more extreme skew of within stream OM fluxes in relation to species body size ranged from `r m_skew_summ %>% slice_min(matches("M.*prob_mean")) %>% select(matches("M.*prob_mean") %>% round(2)` (`r m_skew_summ %>% slice_min(matches("M.*prob_mean")) %>% select(matches("M.*prob_quant2.5") %>% round(2)` -- `r m_skew_summ %>% slice_min(matches("M.*prob_mean")) %>% select(matches("M.*prob_quant97.5") %>% round(2)`) to `r m_skew_summ %>% slice_max(matches("M.*prob_mean")) %>% select(matches("M.*prob_mean")) %>% round(2)` (`r m_skew_summ %>% slice_max(matches("M.*prob_mean")) %>% select(matches("M.*prob_quant2.5")) %>% round(2)` -- `r m_skew_summ %>% slice_max(matches("M.*prob_mean")) %>% select(matches("M.*prob_quant97.5")) %>% round(2)`). Similarly, the probability of a more extremely skewed distribution in relation to population biomass turnover ranged from `r pb_skew_summ %>% slice_min(matches("pb.*prob_mean")) %>% select(matches("pb.*prob_mean")) %>% round(2)` (`r pb_skew_summ %>% slice_min(matches("pb.*prob_mean")) %>% select(matches("pb.*prob_quant2.5")) %>% round(2)` -- `r pb_skew_summ %>% slice_min(matches("pb.*prob_mean")) %>% select(matches("pb.*prob_quant97.5")) %>% round(2)`) to `r pb_skew_summ %>% slice_max(matches("pb.*prob_mean")) %>% select(matches("pb.*prob_mean")) %>% round(2)` (`r pb_skew_summ %>% slice_max(matches("pb.*prob_mean")) %>% select(matches("pb.*prob_quant2.5")) %>% round(2)` -- `r pb_skew_summ %>% slice_max(matches("pb.*prob_mean")) %>% select(matches("pb.*prob_quant97.5")) %>% round(2)`). The probability that energy fluxes were organized randomly or non-randomly in regards to body size showed no clear association with temperature (Figure SX), however, there was a trend towards community energy fluxes becoming more organized (less "randomly" structured) in relation to biomass turnover with increasing temperatures (Figure XX). This relationship exhibited a concave up relationship with temperature, showing a clear trend toward less-random organization from cool to mid-range temperatures and returning towards a more likely random organization at the warmest stream.

The skew of energy fluxes towards populations with smaller/larger body sizes or higher/lower turnover showed weak, yet systematic variation with stream temperature (Figure XX). Skew towards larger body sizes was negatively association with stream temperature. The mean effect size of increasing temperature was to shift the skewness coefficient, $Sk_{flux}$, `r M_skew_temp_coef_mean` units (`r M_skew_temp_coef_quant2.5` to `r M_skew_temp_coef_quant97.5` 95% PI) for every 1 $^\circ$C . The estimated effect of temperature on $Sk_{flux}$ towards higher body size populations exhibited a bimodal distribution around zero, but `r round((sum(M_skew_temp_coefs < 0)/n_boot)*100,1)`% of values fell below zero. Similarly, energy fluxes through the community skewed increasingly toward higher turnover (*P:B*)organisms with increasing temperature. The increase in $Sk_{flux}$ towards higher *P:B* populations was `r pb_skew_temp_coef_mean` (`r pb_skew_temp_coef_quant2.5` to `r pb_skew_temp_coef_quant97.5` 95% PI).

@@

Changing global temperatures are altering the pathways of energy flow across and within ecosystems with potential consequences for the services they provide. Here, we document shifting energy flow pathways across a wide natural temperature gradient to show that increasing mean annual temperatures are associated with reductions in mean community body size and a concomitant increase in mean biomass turnover rates across stream consumer communities. Further, within consumer communities energy fluxes are skewed systematically toward larger, slower-turnover organisms at cooler stream temperatures and smaller
